---
title: "Covid-19 infected cases in the Paris region"
author: "Li"
date: "31/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Discription

This page presents the Covid-19 infected cases in the Paris region, including Paris city and the surrouding departments Seine-et-Marne, Yvelines, Essonne, Hauts-de-Seine, Seine-Saint-Denis, Val-de-Marne, Val-d'Oise. The data contain hospitalized persons, persons under intensive care, deaths and persons being quarantined at home. 
In the map, the size of each circle is proportionnal to the local hospitalized persons number. 

The data are updated on 30/03/2020.

```{r echo=FALSE, message=FALSE}
library(leaflet)


maps <- data.frame(name = c("Paris","Seine-et-Marne", "Yvelines","Essonne", "Hauts-de-Seine","Seine-Saint-Denis", "Val-de-Marne","Val-d'Oise"),
                        hop = c(2217, 468,594, 586,
                                1286,863,1030, 645),
                        death=c(306,45,80,43,127,124,102,127),
                        rea=c(597,138,137,141,293,163,186,137),
                        quarantine=c(607,160,232,133,378,222,299,363),
                   
                        latitude = c(48.857, 48.541648, 48.803738, 48.628779, 48.897384, 48.938199, 48.782199, 49.035560),
                        longitude = c(2.347745, 2.655851, 2.125510, 2.430671, 2.215308,  2.357225,  2.450893,  2.077801))
maps %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(maps$hop) * 200, color='red')%>%
  addMarkers(popup = paste(maps$name,", hospitalized:", maps$hop, ", intensive care:", maps$rea, ", death:", maps$death,  ", quarantine :",maps$quarantine) )

```


